Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-03 eqm_profiles.tex
clean up four cases for patron to invest

Period 1
\begin{enumerate}
	\item Patron: $R_{p1} = \frac{\beta}{1-\de} - \left(q_{s1} - l_{s1}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. Can write in max language.
		\begin{itemize}
			\item International community: 
				\begin{enumerate}
					\item If $R_{p1} + q_{s1} - l_{s1} \geq \frac{\beta}{1-\de}$, $R_{c1} =0$
					\item Otherwise $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right) + \ve$ to augment $l_{s1}$
						\begin{itemize}
							\item (SQ,Cede) is played and game ends
						\end{itemize}
				\end{enumerate}
		\end{itemize}	
	\item Patron might also want to invest to encourage recognition. Most efficient way to do this is to augment $L_{g1}$ (other options are to push either $g$ or $s$ to war, but probability of other outcome diminishes efficiency of investment, and assume payoff to war is lower to begin with).	
\end{enumerate}

>>>>

Period 1
\begin{enumerate}
	\item Patron: $R_{p1} = \frac{\beta}{1-\de} - \left(q_{s1} - l_{s1}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. Can write in max language.
		\begin{itemize}
			\item International community: 
				\begin{enumerate}
					\item If $R_{p1} + q_{s1} - l_{s1} \geq \frac{\beta}{1-\de}$, $R_{c1} =0$
					\item Otherwise $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right) + \ve$ to augment $l_{s1}$
						\begin{itemize}
							\item (SQ,Cede) is played and game ends
						\end{itemize}
				\end{enumerate}
		\end{itemize}	
	\item Patron might also want to invest to encourage recognition directly. How much to augment $l_{g1}$?	
	\item Patron might also want to instigate fighting. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de}$ is positive, invest in $w_{s1}$ to change $\omega_{s1}$. Will not invest in $w_{s1}$ when the quantity is non-positive.
		\begin{itemize}
			\item $c$ will counter up to $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}
